Rectangulotopes

### 2024-04-22 draft/rectangulotopes.tex
fig 2

\begin{figure}
  \includegraphics[width=.9\textwidth]{rectangulations.pdf}
	\caption{Three rectangulations. All three rectangulations are weakly equivalent, but only the first two are strongly equivalent. Only the third one is diagonal.}
	\label{fig:rectequiv}
\end{figure}
\vincent{Add one which is not weakly equivalent?}

>>>>

\begin{figure}
  \includegraphics[width=.9\textwidth]{rectangulations.pdf}
	\caption{Four rectangulations. The leftmost rectangulation is not weakly equivalent to any other. The rightmost three are weakly equivalent, but only the first two are strongly equivalent. Only the third one is diagonal.}
	\label{fig:rectequiv}
\end{figure}
